### 2018-08-07 paper/evaluation.tex
figures!

To evaluate our protocol, we built a prototype of \name that implements all the features previously described but the encryption processes (Sphinxes).
It consists of 5400 lines of Go code.
The users and their behavior (i.e. devices usage and file exchange decisions), on their part, are simulated.
Each device is a Docker container that ships the same \name code, and communicates with its peers via TCP connections.
To allow for realistic simulations (embodying more than 10 users), we distribute the experiments over 5 machines (one with an Intel Xeon E5-2660 CPU (32 cores) and 128GB of RAM, and four having an Intel Xeon E5420 CPU (8 cores) and 32GB of RAM), such that each \squad always resides on the same machine.
All peers are connected to the same Docker overlay network, and are thus reachable from any other device.

@@

\newcommand\trps{\ensuremath{t_{\text{RPS}}}}

@@

\paragraph*{Random Peer Sampling} It has three parameters: the period between two views exchange \trps, set to 400ms, the size of the exchanged views (6) and the size of the devices' view \view, set to 30. 
Using a bigger view would result in more descriptors choice when crafting routes, but their descriptor would be more stale: descriptors in a view have a lifetime of $|\view| * \trps$ seconds on average.

@@

@@

Using the previous parameters, we performed our experiment 30 times, and combined the results to smooth the results, given the variability of the stochastic processes involved (most notably the devices' churn).

>>>>

To evaluate our protocol, we built a prototype of \name that implements the complete \name protocol in 5400 lines of Go code.
The users and their behavior (i.e. devices usage and file exchange decisions), on their part, are simulated by 1500 lines of Python.
Each device is a Docker container that ships the same \name code, and communicates with its peers via TCP connections.
To allow for realistic simulations (embodying more than 10 users), we distribute the experiments over 5 machines (one with an Intel Xeon E5-2660 CPU (32 cores) and 128GB of RAM, and four having an Intel Xeon E5420 CPU (8 cores) and 32GB of RAM), such that each \squad always resides on the same machine.
All peers are connected to the same Docker overlay network, and are thus reachable from any other device.

@@

@@

\paragraph*{Random Peer Sampling} It has three parameters: the period between two views exchange \trps, set to 400ms, the size of the exchanged views (6) and the size of the devices' view \rpsview, set to 30. 
Using a bigger view would result in more descriptors choice when crafting routes, but their descriptor would be more stale: descriptors in a view have a lifetime of $|\rpsview| * \trps$ seconds on average.

@@

Finally, the experiments had a timeout of 15 minutes. 
We observed that downloads---however big---usually succeeded long before this time, or did not succeed whatever time was given to them.

@@

Using the previous parameters, we performed our experiment 30 times, yielding 360 file exchanges. Plots show the aggregation of the results from all experiments, which alleviates the high variability of the stochastic processes involved (most notably the devices' churn).

\begin{figure}[t]
  \centering
  %\def\svgwidth{0.8\columnwidth}
  \includegraphics[width=0.8\columnwidth]{figures/logistic_many_0-001.pdf}

  \caption{\label{fig:logistic}
  Logistic regression of the success rate as a function of the file size using the default parameters.}
\end{figure}

Figure~\ref{fig:logistic} shows the logistic regression of the success rate as a function of the files' size. 
This regression is good candidate to describe binary stochastic processes as a function of a dependent variable,
and is often used in epidemics prediction, economics, and even marketing.
Simply put, given $X$ (in our case, the size of each transfered file) and $y$ (the outcome of the transfer: success or failure), 
the regressor estimates the coefficient $k$ and the mid-point $x_0$ of the logistic function defined as follows:

$$ f(x) = \frac{1}{1 + e^{-k \cdot x + x_0 }} $$

Because it sets the top (100\%) and bottom (0\%) values as asymptotes, 
logistic regression does not yield very optimistic success rates at the beginning,
but its midpoint $x_0$ tends to be very accurate even with a low quantity of training samples.

In our case, $f(x)$ reads the probability that a file exchange fails given its size. 
The plot reads that files below 319MB have more than 90\% chances of being successfully exchanged.
The probability falls as the file gets bigger, such that a 1,O43MB has 50\% chances of successful transfer (see $x_0$).

\subsection{Shortcomings} % (fold)
\label{sub:shortcomings}

There are several aspects in \name that can endanger its security or hinder its performance.
First off, we study the RPS and its capacity to provide a random subset of the whole participants list.

% subsection shortcomings (end)
